---
title: "r for data science 1 ggplot2"
output: html_document
date: '2022-11-02'
---
# Layer and Geometry  
```{r}
library("tidyverse")
ggplot2::mpg
```
```{r}
ggplot(data=mpg)+
  geom_point(mapping=aes(x=displ, y=hwy, colour=class, shape=displ<5), size=2)
```
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), colour='red', size=1.5, shape=20) + 
  facet_grid(drv ~ cyl)
```
```{r}
ggplot(data=mpg) + 
  geom_smooth(mapping=aes(x=displ, y=hwy, linetype=drv))
```
```{r}
ggplot(mpg, mapping=aes(x=displ, y=hwy)) + 
  geom_point(mapping=aes(color=class), show.legend = FALSE) + 
  geom_smooth(color='orange', se=FALSE, linetype="solid")
```
  
# Theme  
Using theme{ggplot2} to set the theme of the coordinate system, such as background, grid and etc.  
  
# Statistic Transformation  
```{r}
ggplot2::diamonds
```
```{r}
ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut, fill=clarity))
#default: stat="count", y=..count...
```
```{r}
ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut, y=..prop.., group=1))
#use y to map a particular computed statistic variables. arguments 'stat="prop"' doesn't work cause there is no stat_prop function.
```
```{r}
ggplot(data=diamonds) + 
  stat_summary(
    mapping=aes(x=cut, y=depth),
    fun.min=min,
    fun.max=max,
    fun=median
  ) + 
  stat_summary(
    mapping=aes(x=cut, y=depth),
    fun=mean,
    color="red"
  )
```
  
# Position and Coordinate System  
Look help for position_dodge, position_fill, position_identity, position_jitter, position_stack.  
Use either position=["dodge"] or position=position_dodg() as argument passed on to the geom layer function.  
  
Look help for COORDINATE_FUNCTION with keyword "coord_" for details.  
  
# The Layered Grammar of Graphics  
Any plot can be described as a combination of a dataset, a geom, a set of mappings, a stat, a position adjustment, a coordinate system, and a facet scheme.  